\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-23 bare_conf.tex
changes from Povilas and languege corrections are merged
Typo fix.

The key part of the proposed system is a smartphone device, connecting User interface (UI) and data processing components into a well-functioning ecosystem. Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet.

>>>>

The key part of the proposed system is a smartphone device, connecting User Interface (UI) and data processing components into a well-functioning ecosystem. Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet.
